---
title: "Iteration and list document"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## List

You can put anything in a list

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE,TRUE, FALSE, TRUE,FALSE,FALSE),
  mat         = matrix(1:8, nrow = 2, ncol = 4),
  summary     = summary(rnorm(1000)))

l
```

```{r}
l$vec_numeric
l[[1]]   #show the first vector in the list, 从结果上，跟l$vec_numeric是一样的
l[[1]][1:3]
mean(l[["vec_numeric"]])
```

## For loop

Create a new list

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(30, 0, 5),
    c = rnorm(40, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)

```

```{r}
list_norms
```

Pause and get my old function

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)){
    stop("Input must be numeric")
  }
  
  if(length(x) < 3){
    stop("Inpur must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
 
}
```

I can apply that function to each list element

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

Let's use a for loop

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norms[[i]])
  
}
```

## Let's try map

```{r}
output = map(list_norms, mean_and_sd)   # 跟for loop效果一样，格式：map(input, function)
output = map(.x = list_norms, ~ mean_and_sd(.x))
```

What if you want a different function..?

```{r}
output = map(list_norms, median)
output = map(list_norms, IQR)   # output as list
```

```{r}
output = map_dbl(list_norms, median) # output 可以以不同格式输出，lec有提及

```

```{r}
output = map_df(list_norms, mean_and_sd) # output 以dataframe格式输出
output = map_df(list_norms, mean_and_sd, .id = "input")   #put the abcd names into a column called "input"
```

## list columns

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```


```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name == "a")
```

Let's try some operation

```{r}
listcol_df$samp[[1]]

mean_and_sd(listcol_df$samp[[1]])
```

Can i just map?

```{r}
map(listcol_df$samp, mean_and_sd)
```

So, can I add a list column???----yes

```{r}
listcol_df = 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd),
         medians = map_dbl(samp, median))

listcol_df
```

## weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Get our list columns

```{r}
weather_nest = 
  weather_df %>% 
  nest(data = date:tmin) # create a new column called "data", is going to result from nesting everything between date and tmin inside each of park station 

weather_nest

weather_nest %>% pull(name)
weather_nest %>% pull(data)

weather_nest$data[[1]]

unnest(weather_nest, cols = data)

weather_nest = 
  weather_df %>% 
  nest(data = date:tmin)
```

Suppose I want to regress tmax on tmin for each station

```{r}
lm(tmax ~ tmin, data = weather_nest$data[[3]])
```

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest$data[[1]])

output = vector("list", 3)

for (i in 1:3){
  output[[i]] = weather_lm(weather_nest$data[[i]])
}
```

Since weather$data is a list, we can apply our weather_lm function to each data frame using map.

```{r}
map(weather_nest$data, weather_lm)
```

```{r}
map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
```

What about a map in a list column!!!?

```{r}
weather_nest = 
  weather_nest %>% 
  mutate(models = map(data, weather_lm)) # add a column called models to save map results

weather_nest
```

