---
title: "make function"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a function to compute z-scores

```{r}
z_scores = function(x) {
  
  if(!is.numeric(x)){
    stop("Input must be numeric")
  }
  
  if(length(x) < 3){
    stop("Inpur must have at least three numbers")
  }
  
  z = (x - mean(x))/sd(x)
  
  return(z)
 
}

z_scores(x_vec)
```

Try my function on some other things. These should give errors

```{r error = TRUE}
z_scores(3) #return NA because sd(3) is NA
z_scores("my name is jeff") # cannot return anything because those are characters
z_scores(mycars) #cannot take a mean of a dataset
z_scores(c(TRUE, TRUE, FALSE, FALSE)) # It works becase R consider them as 1100
```

## Multiple outputs

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)){
    stop("Input must be numeric")
  }
  
  if(length(x) < 3){
    stop("Inpur must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  list(
    mean = mean_x,
    sd = sd_x
  )
 
}

```

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)){
    stop("Input must be numeric")
  }
  
  if(length(x) < 3){
    stop("Inpur must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
 
}
```

Check that the function works

```{r}
x_vec = rnorm(1000)
mean_and_sd(x_vec)
```

## multiple inputs

```{r}
sim_data = 
  tibble(
    x = rnorm(n = 100, mean = 4, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

I'd like to do this with function

```{r}
sim_mean_sd = function(sample_size, miu = 3, sigma = 4){
  sim_data = 
    tibble(
    x = rnorm(sample_size, mean = miu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
  
}

sim_mean_sd(100, 6, 3)
sim_mean_sd(miu = 6, sigma = 7, sample_size = 500) #miu = 6, sigma = 7 rewrite the default numbers
sim_mean_sd(sample_size = 500)#因为default miu = 3, sigma = 4, 所以function can still work

```


Let's do the dynamite sample

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

reviews
```


```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

swm_html = read_html(url)
```

Grab elements that I want

```{r}
# use select gadget to determine what kind of movie title it use
title_vec = 
  swm_html %>% 
  html_nodes(css = ".lister-item-header a") %>% ###".lister-item-header a"这个东西是用gadget 查出来的，每次都不不同
  html_text()

gross_rev_vec = 
  swm_html %>% 
  html_nodes(css = ".a-text-bold span") %>% 
  html_text()

runtime_vec = 
  swm_html %>% 
  html_nodes(css = ".runtime") %>% 
  html_text()

swm_df = 
  tibble(
    title = title_vec,
    gross_rev = gross_rev_vec,
    runtime = runtime_vec
  )

swm_df

```

## Let's review Napoleon Dynamite



```{r, eval = FALSE}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"
dynamite_html = read_html(url)
review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()
review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()
review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()
reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What about the next page of reviews...

Let's turn that code into a function

```{r}
read_page_reviews = function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
    )
  
  reviews
  
}
```

Let me try my function.

```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"
read_page_reviews(dynamite_url)
```

Let's read a few pages of reviews. 

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
dynamite_urls = str_c(dynamite_url_base, 1:50)

all_reviews = 
  bind_rows(
    read_page_reviews(dynamite_urls[1]),
    read_page_reviews(dynamite_urls[2]),
    read_page_reviews(dynamite_urls[3]),
    read_page_reviews(dynamite_urls[4]),
    read_page_reviews(dynamite_urls[5])
  )

all_reviews
```

